---
title: "École d'été 2024 - Introduction"
author: 
  - "Lars Vilhuber"
  - "Marie Connolly"
date: "`r Sys.Date()`"
---
  
```{r, child=c('toc.md')}
```

# Day 1

## Détails {.smaller}

- 13:00 Bienvenue
- 13:15 Description de l'agenda pour les deux jours 
- 13:30 Discussion sur les pré-requis techniques, possiblement formation d'équipes

## Détails {.smaller}

- 13:45 [Day One](https://thnk.ng/day1/)
  - Parcours d'un projet de la conception à l'analyse

## Détails {.smaller}

- 15:15 pause
- 15:30 Description de l'exemple très imparfait 
  - [github.com/labordynamicsinstitute/very-imperfect-example](https://github.com/labordynamicsinstitute/very-imperfect-example)
  - Comment télécharger de Github
  - Répliquons!



# Day 2


```{r, child=c('toc2.md')}
```

## Détails {.smaller}

- 9:00 Discussion de la réussite de l'exercice "Very imperfect example"

- 9:30 Documenting it all: the template README 
  - [https://social-science-data-editors.github.io/template_README/](https://social-science-data-editors.github.io/template_README/)


## Détails {.smaller}

- 10:00 How to run Stata
  - Concept of the working directory 
  - How to dynamically use the working directory
  - Alternatives: here package in other programming languages (Matlab, R), also in Stata 
    - Stata https://github.com/korenmiklos/here 
    - R https://here.r-lib.org/ https://cran.r-project.org/web/packages/rprojroot/rprojroot.pdf 
    - Keep it simple: the right-click method (Windows), the command line method (Mac/Linux)
  - Try it out (30 minutes)
- 10:30 Extra: How to install Stata packages
- 10:45 Break

## Détails {.smaller}

- 11:00 Data provenance
  - Data citations (15 min)
  - Data provenance: beyond citations
    - Complex examples: IPUMS, WDI, DHS
  - Source of the US Census data 
  - Authoritative vs. random sources

## Détails {.smaller}

- 12:00 Break (1h)

## Détails {.smaller}

- 13:00 When data cleaning is critical
  - Your project doesn't start with the analysis data (no "trust me")
  - Find the problem!
  - Try it out: 30 minutes

## Détails {.smaller}

- 13:30 Completing the template README
  - Documenting data provenance
  - The role of licenses and permissions 

  
## Détails {.smaller}

- 14:00 Depositing a replication package
  - Gentle introduction to Zenodo (sandbox) (or Dataverse)
  - Uploading - Zipfiles vs. individual files?
  - Metadata
  - Pressing publish - what happens?
  - Updating a replication package
- 14:30  Break

## Détails {.smaller}

- 14:45 Testing it all
  - So you have it all?
  - Let's try that again: Run your neighbor's replication package in 10 minutes
  - (30 minutes)

## Détails {.smaller}

- 15:15 Wrap-up
  - Group discussion
  - Questions
- 16:00 (ou plus tôt): Fin.


```{r, child=c('toc.md')}
```

